Navigating to a greener Europe with 24/7 hourly clean electricity procurement

### 2023-04-10 manuscript/sections/results.tex
Finish section on diverse grid locations

@@

\cref{fig:10-2025-DEPL-p3-4plots} shows results for the two selected regions: Germany and Poland. Germany is selected as it the largest electricity consumer in Europe and it is well interconnected to regions with clean electrcity grids, such as France and Denmark. 
Poland -- a country with  historic dependency on domestic coal resources, resistance from the coal industry and lack of governmental support for renewable energy -- is selected for a contrast. To keep other factors constant, the same 10\% share of \gls{ci} consumers is set to participate in voluntary clean electricity procurement.\footnote{10\% participation rate of \gls{ci} sector yields load of 3.8~GW in Germany and 1.1~GW in Poland.}

@@

As can be expected, the cleaner grid in the German case results in a lower value of the average emissions rate of participating consumers than in the case of Poland. The values in the reference case are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.\footnote{For reference, 2021 estimates for emission intensity of electricity generation are 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-europa-web}.}

@@

% Another result that stands out in the cases of Germany and Poland is the impact of the 24\7 procurement on the system-level \co emissions.

% Without any CFE procurement stategy, the German power sector carbon emissions are at the level of 40.6 MtCO2 in 2025.

% With just 10\% participation rate, ca. 3.8 GW of C&I load follows voluntary procurement.

% With this participation, the 100\% RES can reduce system-level CO2 emissions by 6 MtCO2 per year. With the 24/7 hourly matching, C&I consumers achieve greater impact on emissions, up to 8 MtCO2 per year with CFE 100\% target.

% NB this impact can be achieved with just a 10\% cost premium on top of the 100\% annual renewable matching (see C&I cost analysis above).

>>>>

\vspace{10pt}
\begin{res}
    Each region of the European electricity system has unique characteristics, such as renewable resources, national policies, degree of interconnection, etc.
    Despite these differences, the model results for 24/7 clean energy procurement show similar trends. 
\end{res}

@@

\cref{fig:10-2025-DEPL-p3-4plots} shows results for the two selected regions: Germany and Poland. Germany is selected as it the largest electricity consumer in Europe and it is well interconnected to regions with clean electrcity grids, such as France and Denmark. 
Poland -- a country with  historic dependency on domestic coal resources, resistance from the coal industry and lack of governmental support for renewable energy -- is selected for a contrast. To keep other factors constant, the same 10\% share of \gls{ci} consumers is set to participate in voluntary clean electricity procurement.%
\footnote{10\% participation rate of \gls{ci} sector yields load of 3.8~GW in Germany and 1.1~GW in Poland.}

@@

As can be expected, the cleaner grid in the German case results in a lower value of the average emissions rate of participating consumers than in the case of Poland. 
The values in the reference case are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.%
\footnote{For reference, 2021 estimates for emission intensity of electricity generation are 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-europa-web}.}

@@

A result that stands out in the cases of Germany and Poland is the impact of the 24/7 hourly CFE procurement on the system-level \co emissions, as shown in \cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions}.
Without any CFE procurement stategy, the German and Polish power sector carbon emissions are at 118.8~Mt\co and 83.8~Mt\co in 2025, respectively.%
\footnote{Germany is a larger electricity consumer, while Polish electricity mix has much a higher emission intensity; thus, power sector carbon emissions are on a similar scale for these regions.} 
If only 10\% of C\&I load joins efforts of voluntary \gls{cfe} procurement, a significant decarbonisation impact is achieved. 
For example in Germany, with this participation, the 100\% annual matching with renewable electricity can reduce system-level \co emissions by 11.1~Mt\co per year. 
With the 24/7 hourly matching, C\&I consumers achieve even greater impact on emissions, up to 14~Mt\co per year with CFE 100\% target.

\cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions} show also similar trends to the base scenario. 
For lower CFE targets, participating consumers can complement portfolio with electricity imports from grid. To achieve higher CFE targets, an clean firm generatorion is added to the portfolio, which greatly reduces the need for renewable generation capacity to match load on an hourly basis. 
In the case of Germany and Poland, both the Allam cycle generator with CCS and advanced dispatchable generator enter the optimal procurement strategy. 
This is likely due to a case that these regions are better interconnected with the rest of the European electrcity grid than Ireland. 
A better interconnection makes possible to exhaust all arbitrage opportunities across time and space and maximise the dispatch value from an advanced dispatchable generator with low variable costs.
